Astronomical Image colorization and up-scaling with Generative Adversarial Networks

### 2021-11-07 Research Paper/CVPR/PaperForReview.tex
Finalized

The problem of colorization of gray scale images with an automated algorithm has been under much research within the machine learning and computer vision communities. Beyond simply being fascinating from an aesthetic and artificial intelligence perspective, such capability has broad practical applications. It is an area of research that possesses great potentials in applications: from black and white photo reconstruction, image augmentation, image enhancement to video restoration for improved interpretability. \\
\hspace*{0.167 in}Image downscaling is an innately lossy process. The principal objective of super resolution imaging is to reconstruct a low resolution image into a high resolution one based on a set of low-resolution images to rectify the limitations that existed while the procurement of the original low-resolution images, insuring better visualization and recognition for scientific and non-scientific purposes. A particularly good up-scaling algorithm will always have some data loss when producing high frequency image due to a downscale-upscale function performed on the image. Ultimately, even the best up-scaling algorithms are unable to effectively reconstruct data that does not exist. Conventional methods rely on low-information and a smooth interpolation between known pixels. These methods can effectively be treated as a convolution with a kernel which encodes no information about the original image. Generative Adversarial Networks (GANs) can be used to hallucinate high frequency data in a super scaled image that does not exist in the smaller image. Even though they increase the resolution of an image, they do not achieve the desired clarity in the super-resolution task. By using the above mentioned method, not a perfect reconstruction can be obtained albeit instead a rather plausible guess can be made at what the lost data might be, constrained to reality by a loss function penalizing deviations from the ground truth image.\\

@@

    		\includegraphics[width=\textwidth]{figures/samples_main}

@@

    		\includegraphics[width=\textwidth]{figures/samples_full-trained}

@@

\hspace*{0.167 in}As noted in \cite{Gao2019astronomical}, a huge number of raw images are present unprocessed and unnoticed in the Hubble Legacy Archives. These raw images, typically black and white, low-resolution, are unfit to be shared with the world. It takes huge amounts of hours to process them. This processing is necessary because it's difficult for astronomers to distinguish objects from the raw images. The processing is further made necessary owing to noise from other bodies in the universe, changing optical characteristics in the system and random \& synthetic noise from the sensors in the telescope. Furthermore, for the process of highlighting small features that ordinarily wouldn't be able to be picked out against noise of the image, we need colorization. The processing of the images is so time consuming that the images are rarely seen by human eyes. Not only is new data being continuously produced by Hubble Telescope, but new telescopes are soon to come online. This goes to show that the problem will likely get worse. A simplification of image processing by using artificial image colorization and super-resolution can be done in an automated fashion to make it easier for astronomers to visually identify and analyze objects in Hubble dataset.

@@

@@

    		\includegraphics[width=\textwidth]{figures/original_sample}

@@

    		\includegraphics[width=\textwidth]{figures/GAN_output_sample}

@@

\hspace*{0.167 in}Levin \etal\cite{levin2004colorization} proposed using colorization hints from the user in a quadratic cost function which imposed that neighboring pixels in space-time with similar intensities should have similar colours. This was a simple but effective method but only had hints which were provided in form of imprecise colored scribbles on the grayscale input image. But with no additional information about the image, the method was able to efficiently generate high quality colorized output. Huang \etal\cite{huang2005edge} addressed the color bleeding issue faced in this approach and solved it using adaptive edge detection. Yatziv \& Sapiro\cite{yatziv2006chrominance} used luminescence based weighting for hints to boost efficiency. Qu \etal\cite{qu2006manga} extended the original cost function to apply color continuity over similar textures along with intensities.

@@

\hspace*{0.167 in}The recent advances in Convolutional Neural Networks have made them a de facto standard for solving image classification problems and their popularity continues to rise with continual improvements. CNNs are peculiar in their ability to learn and differentiate colors, patterns and shapes within an image and their ability to associate them with different classes.\\

@@

\subsubsection{Frequency-domain-based SR image approach}
\hspace*{0.167 in} TSAI \cite{tsai1984multiframe} proposed the frequency domain SR method, where SR computation was considered for the noise free low resolution images. They transformed the low resolution images into Discrete Fourier transform (DFT) and further combined it as per the relationship between the aliased DFT coefficient of the observed low resolution image and that of unknown high resolution image. Then the output is transformed back into the spatial domain where a higher resolution is now achieved.\\
\hspace*{0.167 in} While Frequency-domain-based SR extrapolates high frequency information from the low resolution images and is thus useful, however they fall short in real world applications.

@@

(i) the registration stage for aligning the low-resolution input images,
(ii) the interpolation stage for producing a higher-resolution image, and
(iii) the deblurring stage which enhances thereconstructed high-resolution image produced in the step (ii). \\
\hspace*{0.167 in}However, as each low resolution image adds a few new details before finally deblurring them, this method cannot be used if only a single reference image is available.\\

@@

\hspace*{0.167 in} The Genrative Adversarial Network \cite{goodfellow2014generative}, has two neural networks, the Generator and the Discriminator. These networks compete with each other in a zero-sum game.
Ledig \etal\cite{ledig2017photorealistic} introduced SRGAN in 2017, which used a SRResNet to upscale images with an upscaling factor of 4x. SRGAN is currently the state of the art on public benchmark datasets.

@@

        \includegraphics[width=0.7\textwidth]{figures/gan_visualization.png}

@@

    \hspace*{0.167 in}We started by scraping data off the Hubble Legacy Archive. The scrapper tool %\footnote{Fork: https://github.com/obi-wan-shinobi/hla-scraper}
    which was used, courtesy of Peh \& Marshland \cite{Gao2019astronomical}\footnote{Original repository: https://github.com/KMarshland/hla-scraper}, scraped off hundreds of thousands of colorized images the archive has available. The Hubble Legacy archive is slow and produces grainy images with lots of noise and majority are unprocessed. A filter for M101 (Messier 101) galaxy rendered more than 80 thousand images with a 1 degree difference between consecutive right ascension. The data acquired was large with particularly no efficient way to clean it without human investment. We needed high resolution and well colored images for traning the SRGAN.
    \hspace*{0.167 in}We scraped the Hubble Heritage project instead. The Hubble Heritage project releases the highest-quality astronomical images which are stitched together, colorized and processed to eliminate noise. Heritage then selects the best, most striking of these for public release. However, there were only $\sim150$ of these images that are actually useful. We scraped images from the main Hubble website as well so as to increase the amount of data we had. This provided another $\sim1000$ images approx. Limited by our computational resources, we used images in dimensions of $256\times 256$ pixels with RGB color channels.

@@

    \hspace*{0.167 in}An RGB image is essentially a rank 3 tensor of height, width and color where the last axis contains the color data of our image. The data is represented in RGB color space which has 3 numbers for every pixel indicating the amount of \textit{Red, Green, and Blue} values the pixel has.

@@

    \begin{center}
    	\includegraphics[width=0.45\textwidth]{figures/rgb_colorspace}

@@

    \end{center}

@@

    \begin{center}
    	\includegraphics[width=0.45\textwidth]{figures/Lab_colorspace}
    \end{center}

@@

          G(x) = \hat{y}

@@

         D\big(G(x),y\big) = p

@@

    		\min_{\theta_g}\max_{\theta_d}\Big[\mathbb{E}_{x,y\sim p_{data}} \log D_{\theta_d}(x,y) \\+ E_{{x\sim p_{data}}} \log(1 - D_{\theta_d}(x, G_{\theta_g}(x))\Big]

@@

            \min_{\theta_g}\Big[-\log(D_{\theta_d}(x,G_{\theta_g}(x)))+\lambda \Vert G_{\theta_g}(x) - y \Vert_1 \Big]

@@

    \hspace*{0.167 in}A general solution is proposed in \cite{isola2018imagetoimage} for many image-to-image translation tasks. We propose a similar methodology as proposed in the paper with a few minor tweaks, so as to significantly reduce the amount of training data needed and minimize the training time to achieve similar results. Initially, we propose the use of a U-net for the generator with a pre-trained ResNet-18 network as the \textit{encoder} with half of it's layers clipped off so as to get abstractions from the intermediate layers. It is shown in \cite{ledig2017photorealistic}, that, training the generator separately in a supervised, deterministic manner helps it generalize the mapping from the input space to outputs. The idea solves the problem of \textit{"The blind leading the blind"} that is persistent in most image-to-image translation tasks to date. \\
    \hspace*{0.167 in}The generator is pre-trained independently using the imagenet weights over the Common Objects in Context (COCO) dataset. Unlike adversarial training, this phase was supervised and the loss function used was \textit{mean absolute error} or the \textit{L1 Norm} from the target image. Though trained deterministically,the problem of rectifying incorrect predictions still persists due to constraints over the convergence of loss metric. To combat this, the trained generator was re-trained in an adversarial fashion to help generalize it further. We hypothesize that re-training in an adversarial fashion will further rectify the subtle color differences that \textit{mae} couldn't solve.\\
    \hspace*{0.167 in}A pre-trained ResNet-50 with imagenet weights was used as the discriminator with last few layers clipped off. The discriminative network used is something called a "Patch Discriminator" proposed in \cite{isola2018imagetoimage}. In a \textit{vanilla} discriminator, proposed in \cite{goodfellow2014generative}, the network produces a scalar output, representing the probability that the data $x$ belongs to the input distribution and not the generator distribution $p_g$. Isola \etal\cite{isola2018imagetoimage} proposed a modification to the discriminative network so as to produce, instead of a single scalar, a vector of probabilities representing different localities of the input distribution (image) $x$. For instance, a discriminator producing a $50 \times 50$ vector represents the probabilities every receptive field that is covered by the output vector. Thus, we can localize the corrections in the image that the generator should make.\\

@@

    \hspace*{0.167 in}In the following section, we briefly compare the results of the implemented architectures and evaluate their performance. The evaluation is done qualitatively as well as quantitatively. We compare the performance of each model using L1 and L2 distance between the predictions and targets. Though unreliable, this method provides us with a somewhat decent ground to perform a comparative study and evaluate the reliability of such metrics on GAN evaluation compared to qualitative, visual evaluation. We also measure the performance of the GANs by using Fréchet inception distance (FID) as an attempt to quantify how close the produced images are to the original ones.\\

@@

    		\includegraphics[width=\textwidth]{figures/resnet18_generator_loss}

@@

    		\includegraphics[width=\textwidth]{figures/resnet18_discriminator_loss}

@@

    \Cref{fig: resnet_loss} and \cref{fig: resnet50_disc_loss} shows that the generator converges with a little instability. The discriminator on the other hand oscillates because of the convergence that the generator shows. GAN losses are pretty non-intuitive but we can draw some observations from the loss curves. It seems that the pattern of oscillation and convergence repeats when networks are trained in an adversarial fashion. It is observed that the ResNet U-net with a pre-trained ResNet-18 for its backbone converges decently in the beginning but later shows spikes when nearing the end of training loop. The convergence doesn't signify whether the model is predicting expected results. The loss function just converges to the minimum value that the cost function descends to, permitted by the learning rate. It would normally mean that the GAN has found some optimum point in the vector space that is at the lowest potential and can't decrease any further, meaning the GAN has learned enough. Due to the large number of dimensions, owing to the high amount of trainable variables, such combinations, where the function converges, can be huge in volume. Thus, these numbers don't provide any better understanding of the bias or variance the model is facing. We also discover that even if the loss hasn't converged well doesn't necessarily mean that the model hasn't learned anything. On visual inspection, the generated results show similar distribution to the ground truth, even with high generator losses. This might be due to presence of a content loss parameter in the adversarial loss function which is also minimizing the L1 norm between the generator predictions and target.\\
    \hspace*{0.167 in}The discriminator shows an increase in the objective loss function in the initial epochs and then settles down in the later phase around an oscillation point, converging to some permanent number or rather, oscillating around it. We assume this point to be a point of stability between the two networks as the networks are in a constant adversarial battle, meaning if one performs better, the other is bound to perform worse.

@@

    \hspace*{0.167 in}We present a comparative study of the following models: Basic U-net generator with a custom, residual VGG16 discriminator, hereafter referred to as Basic U-net. A modified U-net with pre-trained ResNet18 as its backbone. We evaluate this model by training it in RGB color space to predict 3 numbers for every pixel and in L*a*b color space where the model predicts the a and b channel alone. We then further train this model to fine-tune it to the task of colorizing astronomical images.

@@

    	\includegraphics[width=0.3\textwidth]{figures/comparison_color}
    	\caption{Results of the colorization study. The first two images in the top row are the ground truth and input image respectively. The next images belong to the output of following, serially: Basic U-net, ResNet18 in RGB colorspace, ResNet18 fine-tuned in L*a*b colorspace, ResNet18 pre-trained U-net in L*a*b colorspace}

@@

    \Cref{color_results} shows that on that particular example, the Basic U-net performs better at predicting results that closely map to the ground truth but the fine-tuned ResNet-18 shows promising results over a larger set of inputs. It can also be observed that the Basic U-net architecture does a decent job of faking the sharpness in the original image and that makes the image appear more realistic as compared to rather blurry outputs from the other networks. \\
    \hspace*{0.167 in}We also observe that the model trained in the RGB color space performs poorly at predicting values of the three color channels and that results in dominance of one channel (blue in this case) over others. This causes the output, though reconstructed quite accurately, to have a varied color pattern with high emphasis on one color channel. This might be because of presence of deep layers which cause gradients of certain colors to diminish over time, causing the model to be strongly biased towards the blue color in this case. An increase in the volume of training data and some random pixel shuffling in forward propagation might solve this problem. \\
    \hspace*{0.167 in}The pre-trained ResNet18 U-net performs decently with the weights gathered by training it over the COCO dataset. The model still lacks the specific coloring intuition in astronomical images and plainly colors specific parts of the images in light colors, leaving majority of the image unaltered. This causes the images to have a 
    grayish tinge

@@

    		\includegraphics[width=\textwidth]{figures/overfit_1}

@@

    		\includegraphics[width=\textwidth]{figures/overfit_2}

@@

    	\caption{Performance of Basic U-net over samples different from the dataset. The left part is the prediction, right part is the ground truth}

@@

    		\includegraphics[width=\textwidth]{figures/samples_pix2pix}

@@

    		\includegraphics[width=\textwidth]{figures/samples_pre-trained}

@@

    		\includegraphics[width=\textwidth]{figures/samples_coco}

@@

    \Cref{color_results} shows that the RGB color space isn't ideal for the task of colorization. In terms of the L1 distance, the best performance is achieved on the ResNet18 U-net with pre-trained weights. This goes to prove the unreliability of distance metrics in model performance evaluation. The model, though quantitatively, performs better than the fine-tuned model but in reality, fails to produce images with visual accuracy. The L2 distance metric shows how the fine-tuned model might, in reality, be fitting slightly better over the data to predict correct color combination as its output. We still consider the results from the fine tuned model to be better than the other performing models and further investigate the per-channel predictions by the model.

@@

    \Cref{tab:channel_wise_results} shows the RGB channel averages of the outputs produced by the fine tuned model. It can be observed that the feature embeddings produced by the model in *a, *b color spaces maps to the green channel with the least error. This might be indicative that the model is performing poorly on images that have a high content of red-blue colors. 

@@

    	\includegraphics[width=0.3\textwidth]{figures/comparison_upscale}

@@

    		\includegraphics[width=\textwidth]{figures/inputsamples_superR}

@@

    		\includegraphics[width=\textwidth]{figures/samples_SRGAN}

>>>>

Colorization of gray scale images with an automated algorithm has been under much research within the machine learning and computer vision communities. Beyond being fascinating from an aesthetic and artificial intelligence perspective, such capability has broad practical applications. It is an area of research that has untapped potential in applications: from black and white photo reconstruction, image augmentation, image enhancement to video restoration for improved interpretability. \\
\hspace*{0.167 in}Image downscaling is an innately lossy process. The principal objective of super resolution imaging is to reconstruct a low resolution image into a high resolution one based on a set of low-resolution images to rectify the limitations that existed while the procurement of the original low-resolution images, insuring better visualization and recognition for scientific and non-scientific purposes. A particularly good up-scaling algorithm will always have some data loss when producing high frequency image due to a downscale-upscale function. Ultimately, even the best up-scaling algorithms are unable to effectively reconstruct non-existing data. Conventional methods rely on low-information and a smooth interpolation between known pixels. These methods can effectively be treated as a convolution with a kernel which encodes no information about the original image. Generative Adversarial Networks (GANs) can be used to hallucinate high frequency data in a super scaled image that does not exist in the smaller image. Even after increasing the resolution, they fail to achieve the desired clarity in the task. By using the above mentioned method, not a perfect reconstruction can be obtained albeit instead a rather plausible guess can be made at what the lost data might be, constrained to reality by a loss function which penalizes deviations from the ground truth image.\\

@@

    		\includegraphics[width=0.8\textwidth]{figures/samples_main}

@@

    		\includegraphics[width=0.8\textwidth]{figures/samples_full-trained}

@@

\hspace*{0.167 in}As noted in \cite{Gao2019astronomical}, a huge number of raw images are unprocessed and unnoticed in the Hubble Legacy Archives. These raw images, typically black and white, low-resolution, are unfit to be shared with the world. It takes huge amounts of hours to process them. This processing is necessary because it's difficult for astronomers to distinguish objects from the raw images and is further made necessary owing to noise from other bodies in the universe, changing optical characteristics in the system and random \& synthetic noise from the sensors in the telescope. Furthermore, for the process of highlighting small features that ordinarily wouldn't be able to be picked out against noise of the image, we need colorization. The processing of the images is so time consuming that the images are rarely seen by human eyes. Not only is new data being continuously produced by Hubble Telescope, but new telescopes are soon to come online. This goes to show that the problem will likely get worse. A simplification of image processing by using artificial image colorization and super-resolution can be done in an automated fashion to make it easier for astronomers to visually identify and analyze objects in Hubble dataset.

@@

    	\begin{subfigure}[b]{0.15\textwidth}

@@

    		\includegraphics[width=0.8\textwidth]{figures/original_sample}

@@

    		\includegraphics[width=0.8\textwidth]{figures/GAN_output_sample}

@@

\hspace*{0.167 in}Levin \etal\cite{levin2004colorization} proposed using colorization hints from the user in a quadratic cost function which imposed that neighboring pixels in space-time with similar intensities should have similar colours. This was a simple but effective method but only had hints provided in form of imprecise colored scribbles on the grayscale input. With no additional information about the image, the method was able to efficiently generate high quality colorized output. Huang \etal\cite{huang2005edge} addressed and solved the color bleeding issue using adaptive edge detection. Yatziv \& Sapiro\cite{yatziv2006chrominance} used luminescence based weighting in hints to boost efficiency. Qu \etal\cite{qu2006manga} extended the original cost function to apply color continuity over similar textures along with intensities.

@@

\hspace*{0.167 in}The recent advances in Convolutional Neural Networks have made them a de facto standard for solving image classification problems. CNNs are peculiar in their ability to learn and differentiate colors, patterns and shapes within an image and their ability to associate them with different classes.\\

@@

@@

(i) the registration stage; aligns the low-resolution input images,
(ii) the interpolation stage; produces a higher-resolution image, and
(iii) the deblurring stage; enhances the reconstructed high-resolution image produced. However, as each low resolution image adds a few new details before deblurring them, this method cannot be used if only a single reference image is available.\\

@@

\hspace*{0.167 in}Ledig \etal\cite{ledig2017photorealistic} introduced SRGAN in 2017, which used a SRResNet to upscale images with an upscaling factor of 4x. SRGAN is currently the state of the art on public benchmark datasets.

@@

        \includegraphics[width=0.7\textwidth]{figures/gan_visualization.pdf}

@@

    \hspace*{0.167 in}The data is scraped off the Hubble Legacy Archive. The scrapper tool %\footnote{Fork: https://github.com/obi-wan-shinobi/hla-scraper}
    which was used, courtesy of Peh \& Marshland \cite{Gao2019astronomical}\footnote{Original repository: https://github.com/KMarshland/hla-scraper}, scraped off hundreds of thousands of colorized images the archive has available. The Hubble Legacy archive is slow and produces grainy images with a lot of noise and majority are unprocessed. A filter for M101 (Messier 101) galaxy rendered more than 80 thousand images with a 1 degree difference between consecutive right ascension. The data acquired was large and with no efficient way to clean it without human investment. We needed high resolution and well colored images for traning the SRGAN. We scraped the Hubble Heritage project instead. The Hubble Heritage project releases the highest-quality astronomical images which are stitched together, colorized and processed to eliminate noise. Heritage then selects the best of these for public release. However, there were only $\sim150$ of these images that were actually useful. We scraped images from the main Hubble website so as to increase the amount of data we had. This provided another $\sim1000$ images approx. Limited by our computational resources, we used images in dimensions of $256\times 256$ pixels with RGB color channels.

@@

    \hspace*{0.167 in}An RGB image is essentially a rank 3 tensor of height, width and color. The data is represented in RGB color space which has 3 numbers for every pixel indicating the amount of \textit{Red, Green, and Blue} values the pixel has.

@@

    \begin{subfigure}[b]{0.4\textwidth}
    	\includegraphics[width=\textwidth]{figures/rgb_colorspace}

@@

    \begin{subfigure}[b]{0.4\textwidth}
    	\includegraphics[width=\textwidth]{figures/Lab_colorspace}
    \caption{Color spaces}

@@

@@

          \footnotesize{G(x) = \hat{y}}

@@

         \footnotesize{D\big(G(x),y\big) = p}

@@

    \min_{\theta_g}\max_{\theta_d}\Big[\mathbb{E}_{x,y\sim p_{\tiny{data}}} \log D_{\theta_d}(x,y) \\+ E_{{x\sim p_{\tiny{data}}}} \log(1 - D_{\theta_d}(x, G_{\theta_g}(x))\Big]

@@

            \footnotesize{\min_{\theta_g}\Big[-\log(D_{\theta_d}(x,G_{\theta_g}(x)))+\lambda \Vert G_{\theta_g}(x) - y \Vert_1 \Big]}

@@

    \hspace*{0.167 in}A general solution is proposed in \cite{isola2018imagetoimage} for many image-to-image translation tasks. We propose a similar methodology with a few minor tweaks, so as to significantly reduce the amount of training data needed and minimize the training time to achieve similar results. Initially, we propose the use of a U-net for the generator with a pre-trained ResNet-18 network as the \textit{encoder} having half of it's layers clipped off so as to get the intermediate abstractions. It is shown in \cite{ledig2017photorealistic}, that, training the generator separately in a supervised, deterministic manner generalizes the mapping from the input space to outputs. The idea solves the problem of \textit{"The blind leading the blind"} that is persistent in most image-to-image translation tasks to date. \\
    \hspace*{0.167 in}The generator is pre-trained independently using the imagenet weights over the COCO dataset. Unlike adversarial training, this phase was supervised with \textit{mean absolute error} or the \textit{L1 Norm} as the loss from the target image. Though trained deterministically,the problem of rectifying incorrect predictions still persists due to constraints over the convergence of loss metric. To combat this, the trained generator was re-trained in an adversarial fashion for further generalization. We hypothesize that re-training in an adversarial fashion will further rectify the subtle color differences that \textit{mae} couldn't solve.\\
    \hspace*{0.167 in}A pre-trained ResNet-50 with imagenet weights was used as the discriminator with last few layers clipped off. The discriminative network used is something called a "Patch Discriminator" proposed in \cite{isola2018imagetoimage}. In a \textit{vanilla} discriminator, proposed in \cite{goodfellow2014generative}, the network produces a scalar output, representing the probability of the data $x$ belonging to the input distribution and not the generator distribution $p_g$. Isola \etal\cite{isola2018imagetoimage} proposed a modification to the discriminative network so as to produce, instead of a single scalar, a vector of probabilities representing different localities of the input distribution (image) $x$. For instance, a discriminator producing a $50 \times 50$ vector represents the probabilities every receptive field that is covered by the output vector. Thus, we can localize the corrections in the image that the generator should make.\\

@@

    \hspace*{0.167 in}In the following section, we compare the results of the implemented architectures and evaluate their performance. The evaluation is done qualitatively as well as quantitatively by comparing the performance of each model using L1 and L2 distance between the predictions and targets. Though unreliable, this method provides us with a somewhat decent ground to perform a comparative study and evaluate the reliability of such metrics on GAN evaluation compared to qualitative, visual evaluation. The performance of the GANs is also measured by using Fréchet inception distance (FID) as an attempt to quantify how close the produced images are to the original ones.\\

@@

    		\includegraphics[width=0.8\textwidth]{figures/resnet18_generator_loss}

@@

    		\includegraphics[width=0.8\textwidth]{figures/resnet18_discriminator_loss}

@@

    \Cref{fig: resnet_loss} and \cref{fig: resnet50_disc_loss} shows that the generator converges with a little instability. The discriminator on the other hand oscillates because of the convergence that the generator shows. GAN losses are pretty non-intuitive but we draw a few conclusions from the graphs. This pattern of oscillation and convergence repeats when networks are trained in an adversarial fashion. It is observed that the generator with a pre-trained ResNet-18 for its backbone converges decently in the beginning but later shows spikes when nearing the end of training loop. The convergence doesn't signify whether the model is predicting expected results. The loss just converges to the minimum value that the cost function descends to, permitted by the \textit{lr}. It would normally mean that the GAN has found some optimum point in the vector space that is at the lowest potential and can't decrease any further, meaning the GAN has learned enough. Due to the sheer no. of dimensions, owing to the high amount of trainable variables, such combinations, where the function converges, can be high in volume. Thus, these numbers don't provide any better understanding of the bias or variance the model is facing. We also discover that even if the loss hasn't converged well it doesn't necessarily mean that the model hasn't learned anything. On visual inspection, the generated results show similar distribution to the ground truth, even with high generator losses. This might be due to presence of a content loss parameter in the adversarial loss function which is also minimizing the L1 norm between the predictions and target.\\
    \hspace*{0.167 in}The discriminator shows an increase in the objective loss in the initial epochs, settles down in the later phase around a point, converging to some permanent number and oscillating around it. We assume this point to be a point of stability between the two networks as the networks are in a constant adversarial battle, meaning if one performs better, the other is bound to perform worse.

@@

    \hspace*{0.167 in}We present a comparative study of the following models: Basic U-net generator with a residual VGG16 discriminator, hereafter referred to as Basic U-net. A modified U-net with pre-trained ResNet18 as it's backbone. We evaluate the model by training it in RGB colorspace to predict 3 \textit{nos.} for every pixel and in L*a*b colorspace where the model predicts the a and b channel alone. We then further fine-tune this model to the task of colorizing astronomical images.

@@

    	\includegraphics[width=0.27\textwidth]{figures/comparison_color}
    	\caption{Results of the colorization study.From top left, (1) the ground truth and (2) input image. The next images belong to the output of following, serially: Basic U-net, ResNet18 in RGB, ResNet18 fine-tuned in L*a*b, ResNet18 pre-trained U-net in L*a*b}

@@

    \Cref{color_results} shows that on a particular example, the Basic U-net performs better at predicting results that closely map to the ground truth even if the fine-tuned ResNet-18 shows better results for larger set of inputs. It can also be observed that the Basic U-net architecture does a decent job of faking the sharpness in the original image and that makes the image appear more realistic as compared to rather blurry outputs from the other networks. \\
    \hspace*{0.167 in}We also observe that the model trained in the RGB color space performs poorly at predicting values of all color channels and that results in channel bias (blue in this case). This causes the output, though reconstructed quite accurately, to have a varied color pattern with high emphasis on one color channel. This might be caused by the deep layers which result in diminishing gradients for certain colors over time, causing the model to be strongly biased towards the blue color in this case. An increase in the volume of training data and some random pixel shuffling in forward propagation might solve this problem. \\
    \hspace*{0.167 in}The pre-trained ResNet18 U-net performs decently with the weights gathered by training it over the COCO dataset. The model still lacks the specific coloring intuition in astronomical images and plainly colors specific parts of the images in light colors, leaving majority of the image unaltered. This causes the images to retain grayness.

@@

    		\includegraphics[width=0.9\textwidth]{figures/overfit_1}
    		\caption{Sample 1}

@@

    		\includegraphics[width=0.9\textwidth]{figures/overfit_2}

@@

    	\caption{Performance of Basic U-net over samples different from the dataset. Left: prediction, right: ground truth}

@@

    		\includegraphics[width=0.7\textwidth]{figures/samples_pix2pix}

@@

    		\includegraphics[width=0.7\textwidth]{figures/samples_pre-trained}

@@

    		\includegraphics[width=0.7\textwidth]{figures/samples_coco}

@@

    \Cref{color_results} shows that the RGB colorspace isn't ideal for the task of colorization. In terms of the L1 distance, the best performance is achieved by ResNet18 U-net with pre-trained weights. This goes to prove the unreliability of distance metrics in performance evaluation. The model, though quantitatively, performs better than the finetuned model but in reality, fails to produce visually convincing images. The L2 distance metric shows how the fine-tuned model might, in reality, be fitting slightly better over the data to predict correct color combination as its output. We further investigate the per-channel predictions by the model.

@@

    \Cref{tab:channel_wise_results} shows the RGB channel averages of the outputs produced by the fine tuned model. It can be observed that the feature embeddings produced by the model in *a, *b colorspaces maps to the green channel with the least error. This could indicate that the model performance is poor on images with high content of red-blue colors. 

@@

    	\includegraphics[width=0.27\textwidth]{figures/comparison_upscale}

@@

    		\includegraphics[width=0.75\textwidth]{figures/inputsamples_superR}

@@

    		\includegraphics[width=0.75\textwidth]{figures/samples_SRGAN}
